Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
lc

In contrast to multilayer networks formed by combining layers defined
by different types of interactions, multilayer networks with GPS data are limited to 
proximity based measures. An alternative which has been explored is using 
hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]

<!-- types of relationships, ML nets -->
<!-- GPS caveat HMM -->

Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a].

For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015]. With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017].

Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca
mulatta*) had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences. Multilayer networks provide the opportunity to
address these types of questions involving social scale with all the individual
layers of interaction integrated in a holistic way.

social scale results

## Social scale

Social scale is a major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015]. With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the winter,
individuals demonstrate dramatically different graph strength (Figure 
\@ref(fig:socres)) in different habitat types, having higher graph strength in
forage and open habitats where they can likely see each other and still interact
with visual cues unlike in forest habitats. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca
mulatta*) had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences. Multilayer networks provide the opportunity to
address these types of questions involving social scale with all the individual
layers of interaction integrated in a holistic way.

@@

Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality across scales.

@@

## Etc

>>>>

Social structure and habitat selection are intimately linked: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
novel framework for considering the influence of habitat selection and space use
on sociality.

Given that habitat data are available across a wide range of spatial scales, we
evaluated the influence of spatial resolution on multilayer network metrics. The
results indicate varied influence of increasing spatial resolution depending on
the habitat layer. As spatial resolution increased, edge overlap decreased in
forage while remaining stable in open and forest habitats (Figure
\@ref(fig:socres) D). Forage is a rare and patchy habitat on Fogo Island, as is
indicated by a decrease in the proportion of relocations in this habitat type
with increasing spatial resolution (Figure S1)<!--TODO-->. Similar to increasing
spatial distance threshold, the influence of increasing spatial resolution on
graph strength was notably different between habitat layers. Forest layers
showed little change in graph strength with increasing spatial resolution and
variation between individuals. Forage and open layers had greater individual
variation in graph strength, while forage was the sole layer to show large
responses in graph strength to increasing spatial resolution (Figure
\@ref(fig:socres) E). As such, multilayer network measures related to habitat
are explicitly dependent on spatial scale. Edge overlap can indicate if some
associations between individuals are dependent on the habitat-context
[@Battiston_2014]. If the spatial resolution of the habitat data are
insufficient to capture rare habitats, context-specific relationships between
individuals may not be captured by multilayer networks.

<!-- Multilayer network extensions:
movement

@@

GPS caveat HMM

Multilayer networks can be built with different types of interactions, a differ
In contrast to multilayer networks formed by combining layers defined
by different types of interactions, multilayer networks with GPS data are limited to 
proximity based measures. An alternative which has been explored is using 
hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
-->

@@

## Etc
<!-- soc -->
Social scale is a major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015]. With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the winter,
individuals demonstrate dramatically different graph strength (Figure 
\@ref(fig:socres)) in different habitat types, having higher graph strength in
forage and open habitats where they can likely see each other and still interact
with visual cues unlike in forest habitats. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca
mulatta*) had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences. Multilayer networks provide the opportunity to
address these types of questions involving social scale with all the individual
layers of interaction integrated in a holistic way.
